Convective heat transport in stratified atmospheres at low and high Mach number

### 2017-03-07 tex/nusselt_paper.tex
makes tex file mostly fit into an 80-column terminal.  Adds King&all ref

%%%%% Body of the paper
\section{Introduction}
\refstepcounter{section}
\label{sec:intro}
Convection transports energy in stellar and planetary atmospheres.
In these objects, flows are compressible and
feel the atmospheric stratification.  While in some systems this stratification is
negligible, it is significant in regions such as
the convective envelope of the Sun, which spans 14 density scale heights.
In the bulk of these systems, flows are at very low Mach Number (Ma), but numerical
constrainst have restricted most studies of compressible convection to high Ma.
These studies have provided important insight into the low temperature, high Ma region
near the Sun's surface, but few fundamental
properties of low Ma convection which characterize deeper motions
are known.

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
\caption{The mean adiabatic Mach number of long-time-averaged profiles
is shown.  Error bars show the full range of Ma over the depth of the
atmosphere.
(a) When $Ma < 1$ (below the black horizontal line), Ma $\propto \epsilon^{1/2}$.
at low ($10^2$) and moderate ($10^5$) values of Ra.
(b) When Ra is small, Ma $\propto Ra^{1/2}$ (dashed lines).
Once the mean Ma reaches 1 ($\epsilon = \{0.5, 1\}$), this scaling breaks down
and nearly all flows in the atmosphere are at Ma = 1.
At low $\epsilon$, a consistent power law of Ma $\propto Ra^{1/4}$ is retrieved.
\label{fig:ma_v_eps} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
\caption{
Variation of Nu as Ra increases at high and low $\epsilon$. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime is evident in the scaling
of Nu with Ra at $\text{Ra}_{\text{top}} \approx 10^4$.  In the low $\epsilon$ regime (green diamonds and yellow squares), 
our observed Nu scalings collapse onto a similar line which is
indistinguishable from a $\text{Ra}_{\text{top}}^{2/7}$ scaling, 
as observed in RB convection \cite{johnston&doering2009}.  Error bars are determined
 by the square root of the variance of the time-averaged Nu profile with depth and 
 indicate whether or not a solution is well-converged.
 \label{fig:re_and_nu_v_ra}.
}
\end{figure}

@@

The variation of Nu with Ra$_{\text{top}}$ is shown in Fig. \ref{fig:re_and_nu_v_ra}a.
At low to moderate Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$ (NEED TO CITE A
RB PAPER WITH A 1/3 POWER LAW \cite{ahlers&all2009} maybe?).  At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ at $\epsilon = 0.5$.
The scaling of Nu with Ra$_{\text{top}}$ is unclear at low $\epsilon$ (so I'll try to fill in that space with
data from comps...time to fish it out of Lou and do post-processing hell).

@@

As the thermodynamic variables converge to their steady state values, the density
profile evolves while remaining in hydrostatic equilibrium to zeroth order.  In 
Fig. \ref{fig:nrho_v_ra} we show the number of density scale heights present in the
evolved solution using two measures.  We find that once the average Ma of the domain
becomes approximately one, large density inversions begin to form in the boundary layers,
as was reported by \cite{brandenburg&all2005}.  The Regardless, the agreement of Nu
across $\epsilon$ despite the different effective stratifications felt in the simulations
is striking.

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133 (\textbf{AND ALSO THE NEW ONE AS OF 2017}).
We thank Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi for many useful discussions.

>>>>

%%%%% Body of the paper
\section{Introduction}
\refstepcounter{section}
\label{sec:intro}
Convection transports energy in stellar and planetary atmospheres.
In these objects, flows are compressible and
feel the atmospheric stratification.  While in some systems this stratification 
is negligible, it is significant in regions such as
the convective envelope of the Sun, which spans 14 density scale heights.
In the bulk of these systems, flows are at very low Mach Number (Ma), 
but numerical constraints have restricted most studies of 
compressible convection to high Ma.
These studies have provided important insight into the low temperature, 
high Ma region near the Sun's surface, but few fundamental
properties of low Ma convection which characterize deeper motions
are known.

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/ma_v_Ra.png}
\caption{The mean adiabatic Mach number of long-time-averaged profiles
is shown.  Error bars show the full range of Ma over the depth of the
atmosphere.
(a) When $Ma < 1$ (below the black horizontal line), 
Ma $\propto \epsilon^{1/2}$.
t low ($10^2$) and moderate ($10^5$) values of Ra.
(b) When Ra is small, Ma $\propto Ra^{1/2}$ (dashed lines).
Once the mean Ma reaches 1 ($\epsilon = \{0.5, 1\}$), this scaling breaks down
and nearly all flows in the atmosphere are at Ma = 1.
At low $\epsilon$, a consistent power law of Ma $\propto Ra^{1/4}$ is retrieved.
\label{fig:ma_v_eps} }
\end{figure}

@@

\begin{figure}[t]
\includegraphics[width=3.4375in]{./figs/re_and_nu_v_Ra.png}
\caption{
Variation of Nu as Ra increases at high and low $\epsilon$. 
At high $\epsilon$ (purple circles), 
a clear transition from the subsonic to supersonic regime 
is evident in the scaling
of Nu with Ra at $\text{Ra}_{\text{top}} \approx 10^4$.  
In the low $\epsilon$ regime (green diamonds and yellow squares), 
our observed Nu scalings collapse onto a similar line which is
indistinguishable from a $\text{Ra}_{\text{top}}^{2/7}$ scaling, 
as observed in RB convection \cite{johnston&doering2009}.  
Errors bars indicate the properly normalized range of the
value of Nu as a function of depth and
large error bars indicate a poorly converged solution.
 \label{fig:re_and_nu_v_ra}.
}
\end{figure}

@@

The variation of Nu with Ra$_{\text{top}}$ is shown in 
Fig. \ref{fig:re_and_nu_v_ra}a.
At low to moderate Ra$_{\text{top}}$, 
Nu $\propto$ Ra$_{\text{top}}^{1/3}$ regardless of $\epsilon$,
as predicted by classical \RB theory \cite{king&all2012}.
At large Ra$_{\text{top}}$, Nu $\propto$ Ra$_{\text{top}}^{1/5}$ 
at $\epsilon = 0.5$.
The scaling of Nu with Ra$_{\text{top}}$ 
is unclear at low $\epsilon$ (so I'll try to fill in that space with
data from comps...time to fish it out of Lou and do post-processing hell).

@@

As the thermodynamic variables converge to their steady state values, 
the density profile evolves while remaining in hydrostatic equilibrium 
to zeroth order.  In Fig. \ref{fig:nrho_v_ra} we show the number of density 
scale heights present in the evolved solution using two measures.  
We find that once the average Ma of the domain
becomes approximately one, large density inversions begin to 
form in the boundary layers, as was reported by \cite{brandenburg&all2005}.  
Regardless, the agreement of Nu across $\epsilon$, particularly at
low Ra, despite the difference in effective stratifications is striking.

@@

\subsection{acknowledgements}
EHA acknowledges the support of the University of Colorado's George 
Ellery Hale Graduate Student Fellowship.
This work was additionally supported by  NASA LWS grant number NNX16AC92G.  
Computations were conducted 
with support by the NASA High End Computing (HEC) Program through the NASA 
Advanced Supercomputing (NAS) Division at Ames Research Center on Pleiades
with allocations GID s1647 and GID g26133.
We thank Jon Aurnou, Axel Brandenburg, Keith Julien, Mark Rast, and Jeff Oishi 
for many useful discussions.
